Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Power Spectra

### 2025-06-17 paper/main.tex
update manuscript; adjust plot for sims

Notice, in the center/right panels of Figure \ref{fig:plot_data}, the precision of each
low/high resolution spectra increases as $k$ increases.  The curves get progressively 
tighter from left to right.  We would like to conveniently wrap this domain-specific 
knowledge inside our Bayesian framework later.  To this end, \cite{moran2023mira} 
used the multiple low- and high-resolution spectra across all cosmologies to
obtain precision estimates, $p_1,\dots, p_n$, across the $n$ 
wavenumber values using a log-log regression model. A multiplier $c$ for 
the increase in precision from the low- to high- resolution output is also 
estimated with this regression model. 
\textcolor{red}{(What is the c value?  Can we report it?)}
We use these estimates to define three 
diagonal precision matrices, one for each data type (perturbation theory, 
low resolution average, and high resolution). Specifically, denote $\Lambda_p$, 
$\Lambda_\ell$, and $\Lambda_h$ as the $n\times n$ diagonal matrices with elements
\[
\Lambda_p^{(ii)} = \begin{cases}
    10^5 &\text{for } k_i < 0.04 \\
    0  &\text{otherwise}\\
    \end{cases}
\quad
\Lambda_\ell^{(ii)} = \begin{cases}
    16p_i &\text{for } 0.04 \leq k_i < 0.25 \\
    0  &\text{otherwise}\\
    \end{cases}
\quad
\Lambda_h^{(ii)} = \begin{cases}
    cp_i &\text{for } 0.04 \leq k_i < 5 \\
    0  &\text{otherwise}\\
    \end{cases}
\]
for $i=1,\dots, n$.  In $\Lambda_p$, we use the sufficiently high precision 
of $10^5$ to impose the deterministic nature of the perturbation theory output.
In $\Lambda_\ell$, the multiplication by 16 accounts for the sample size of the
low resolution runs.
We then calculate a weighted average for each cosmology: 
$\bar y = \Lambda^{-1}(\Lambda_p y_p + \Lambda_{\ell} \bar{y}_\ell + \Lambda_h y_h)$, 
where $\Lambda = \Lambda_p + \Lambda_\ell + \Lambda_h$ and 
$\bar{y}_\ell = \frac{1}{16}\sum_{r=1}^{16} y_{\ell_r}$. In Figure \ref{fig:plot_data},
the weighted average is shown in dashed orange.  As an estimate of the true
underlying spectrum, the weighted average fluctuates too drastically.  
This is especially apparent after centering (right panel).
\textcolor{red}{(@Steve - how are we centering?)}
Although the weighted average incorporates all available observatons and 
expert knowledge regarding the precisions, it fails to account for the spatial 
dependence inherent in the smooth but stochastic spectra, which is pivotal to 
effectively inferring the true spectrum.

@@

\subsection{Model Specification}

@@

For both $\Sigma_S$ and $\Sigma_W$, we use Mat\`ern kernels with unit scale and
unique lengthscales,
\[
\begin{array}{l}
\Sigma_S(W)^{i,j} = k\left(||w_i - w_j||^2, \theta_S\right) \\[7pt]
\Sigma_W(X)^{i,j} = k\left(||x_i - x_j||^2, \theta_W\right)
\end{array}
\quad\textrm{where}\quad
k(d, \theta) = \left( 1 + \frac{\sqrt{5}d}{\sqrt{\theta}} + 
  \frac{5d^2}{3\theta}\right) \exp\left(-\frac{\sqrt{5}d}{\sqrt{\theta}}\right).
\]
In our one-dimensional setting, we embrace unit scale on $S$ to preserve parsimony 
and identifiability with $\theta_S$ \textcolor{red}{(@Steve - can you cite that paper here?)}.
Unit scale on latent $W$ was recommended by \citet{sauer2023active} for similar reasons.

@@

We compare DGP.FCO to competing models with a simulation study where the underlying 
true curve is known. Following \cite{moran2024dpc}, we consider two functions 
($f_1$ and $f_2$) each with two variance specifications (settings ``A" and ``B", 
\textcolor{magenta}{we can consider additional homoskedastic cases in the appendix if necessary}).

Here, $f_1$ and $f_2$ are defined as follows:
\begin{align}
  f_1(x) &= m_1 \exp(-u_1x/2) * \cos(wx) - m_1x/5, \quad w=\sqrt{25-[u_1/2]^2} \\
  f_2(x) &= \exp(-m_2[x-3]^2)+\exp(-u_2[x-1]^2)-0.05\sin(8[x-1.9]), \\ 
  \quad x &\in [0,4].
\end{align}

For additional variation, the values of $m_1, m_2, u_1,$ and $u_2$ are random where 
$m_1 \sim \text{Uniform}(0.5,1.5)$, $u_1 \sim \text{Uniform}(1.5,2.5)$, and $m_2,u_2 
\sim \text{Uniform}(0.6,1.4)$.

For the two variance settings, we consider matrices $\Sigma_A$ and $\Sigma_B$ to 
have a Mat\'ern covariance function with a nugget of $10^{-8}$ and smoothness of 2.5. 
For setting ``A", we have $\tau^2=0.0225$ and $\theta=0.01$. For setting ``B", we have 
$\tau^2=0.1$ and $\theta=0.05$, and additionally scale this covariance matrix by 
a vector of precision values $s$ so that $\Sigma_B = s M s^T$ is nonstationary; here $M$ is 
a Mat\'ern covariance matrix with parameters $\tau^2$ and $\theta$.

For each simulated function and variance specification, we generate 20 values of 
$m_1, m_2, f_1, f_2$, and conditional on these values, we sample either 5 or 15 
functional observations and estimate the underlying true function based on the observations.

\begin{figure}[t]
    \centering
    \includegraphics[width=6in]{sims_logS.png}
    \caption{Boxplot of log scores across two different functions and covariance 
             settings (lower is better). For each case, the boxplot is constructed 
             from 20 random batches were simulated. Each column represents a function/variance 
             specification pair, and each row shows results for batch sizes of either 
             5 (top) or 15 (bottom).}
    \label{fig:sims_logS}
\end{figure}

The competing methods we consider are an out-of-the-box DGP fit using the 
\texttt{deepgp} package \citep{sauer2023active}, a heteroskedastic GP fit using 
the \texttt{hetGP} package \citep{binois2018practical, binois2021hetgp}, as well 
as a deep process convolution (DPC) approach, which is utilized within Cosmic 
Emu \citep{moran2023mira}.

The metrics we use to evaluate performance are mean squared error (MSE) and the 
log score, a proper scoring rule which takes both prediction and intervals into 
consideration \citep{gneiting2007strictly}. For both metrics, a lower value indicates 
better performance. Log score are shown in Figure \ref{fig:sims_logS}; our DGP.FCO 
model performs favorably against each of these current benchmark methods by
accounting for spatial dependence within our model, resulting in more accurate UQ.
MSE results, which do not address UQ, were comparable across competing methods; these results
can be found in Figure \ref{fig:sims_MSE}. \textcolor{magenta}{If we mention that DGP.FCO timings 
speed up compared to \texttt{deepgp} and DPC, we would also need to mention that \texttt{hetGP} 
is much faster than all of these.}

@@

In addition to simulated data, we investigate model fits for different cosmological 
datasets from CAMB \citep{lewis2011CAMB}. These datasets contain power spectra based
on six-dimensional cosmological parameter settings. Similar to the Mira-Titan suite, the
CAMB dataset has multiple (sixty-four) batches of power spectra for each cosmology, with each batch 
containing multiple (fifteen) low-resolution spectra, and one high-resolution sprectum. 
Unlike the Mira-Titan suite, this dataset favorably contains an infinite-resolution 
spectrum, which can be treated as the true spectrum for each cosmology,
allowing us to accurately assess posterior mean estimates and credible intervals.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{CAMB_fit_model1.png}
    \caption{Example of DGP.FCO model fit for the first batch of model runs from the CAMB data, 
             with LOESS mean term subtracted. We can compare the orange lines 
             (posterior mean and dotted 95\% credible interval) to the light blue line,
             representing the infinite-resolution ``true" spectrum.}   
    \label{fig:fit_camb}
\end{figure}

We use 32 CAMB batches to train the DGP.FCO model and reserve the other 32 as a test set.
To imitate the role of the perturbation theory output of Mira-Titan, we anchor estimates of the CAMB
power spectrum at the infinite-resolution for $\log_{10}(k) < -1.7$, and then rely 
strictly on the low- and high-resolution runs for $k$ above this. We take a weighted
average of the CAMB runs and assume heteroskedastic errors in a similar fashion.

We use a log-log regression model to obtain precision estimates $\Lambda_\ell$ and $\Lambda_h$
for the low- and high-resolution runs respectively, as outlined in Section \ref{sec:data}. 
Similarly, we set $\Lambda_i=10^8$ to illustrate high confidence in the infinite-resolution 
run for low $k$ values and incorporate these estimates within $\Sigma_\varepsilon$. 
With the precision information, we then estimate the Mat\'ern parameters for 
$\Sigma_\varepsilon$. For the CAMB data, lengthscale estimates are consistently 
around $3\times 10^{-7}$, evidence that we can simplify our covariance structure 
to contain no spatial dependence (compare low-resolution runs of Figure \ref{fig:fit_camb} 
with Figure \ref{fig:plot_data}). We therefore specify $\Sigma_\varepsilon = 
(15\Lambda_\ell+\Lambda_h+\Lambda_i)^{-1}$ for the CAMB data.

@@

@@

From plots of the multiple low-resolution spectra (e.g., Figure \ref{fig:plot_data}), 
we find they vary smoothly about some mean $S$, suggesting that a dense covariance 
matrix $\Sigma_\varepsilon$ (accounting for spatial dependence) may outperform a 
diagonal covariance $\Lambda_\ell^{-1}$ for $\bar Y$. From Section \ref{sec:data},
we can incorporate domain knowledge from $\Lambda_p, \Lambda_\ell,$ and $\Lambda_h$ 
within our model. In previous work, we have modeled multiple candidates for 
$\Sigma_\varepsilon$ \citep{walsh2023bayesian} and found that a Mat\'ern covariance 
$\Sigma_\ell$ trained on the low-resolution runs (pre-scaled by the precision 
values and subtracting a LOESS-smoothed average) performs the best. 
We specify this structure within $\Sigma_\varepsilon$ and refer readers 
to \cite{walsh2023bayesian} for a more detailed exposition. This yields 
$\Sigma_\varepsilon=\left(\Lambda_p^{-1} + \Sigma_\ell + \Lambda_h^{-1}\right)^{-1}$, 
where $\Lambda_p, \Sigma_\ell^{-1}, \text{ and } \Lambda_h$ are all $n\times n$ 
and are 0 wherever the corresponding data type is biased. From here, we estimate 
$\tau_\ell, \theta_\ell$ with maximum likelihood, and input these within 
$\Sigma_\varepsilon$, which we use as an input to our model.

@@

From these samples, we can estimate and quantify the uncertainty within each 
cosmology's average and latent layer $W$. Figure \ref{fig:plot_fit} shows an 
example of the uncertainty for our posterior mean for the first (of 111) training 
cosmologies; the posterior mean is subtracted in order to visualize this uncertainty. 
Figure \ref{fig:plot_warp} provides elliptical slice samples of $W$ along with the 
average warping. Some departure from stationarity is estimated in the higher $X$ 
(i.e., scaled $k$) values.

@@

\begin{figure}[ht]
   \centering
   \includegraphics[width=6in]{plot_warp_M001.png}
   \caption{Left: MCMC samples of $W$ for model M001 after burnin and thinning. 
            Right: Corresponding 95\% credible intervals for $W$, where departure 
            from the identity line represents nonstationary behavior.}
   \label{fig:plot_warp}
\end{figure}

>>>>

Notice, in the center/right panels of Figure \ref{fig:plot_data}, the precision of each
low/high resolution spectra increases as $k$ increases.  The curves get progressively 
tighter from left to right.  We would like to conveniently wrap this domain-specific 
knowledge inside our Bayesian framework later.  To this end, \cite{moran2023mira} 
used the multiple low- and high-resolution spectra across all cosmologies to
obtain precision estimates, $p_1,\dots, p_n$, across the $n$ 
wavenumber values using a log-log regression model. A multiplier $c\approx 3.73$ for 
the increase in precision from the low- to high- resolution output is also 
estimated with this regression model. 
We use these estimates to define three 
diagonal precision matrices, one for each data type (perturbation theory, 
low resolution average, and high resolution). Specifically, denote $\Lambda_p$, 
$\Lambda_\ell$, and $\Lambda_h$ as the $n\times n$ diagonal matrices with elements
\[
\Lambda_p^{(ii)} = \begin{cases}
    10^5 &\text{for } k_i < 0.04 \\
    0  &\text{otherwise}\\
    \end{cases}
\quad
\Lambda_\ell^{(ii)} = \begin{cases}
    16p_i &\text{for } 0.04 \leq k_i < 0.25 \\
    0  &\text{otherwise}\\
    \end{cases}
\quad
\Lambda_h^{(ii)} = \begin{cases}
    cp_i &\text{for } 0.04 \leq k_i < 5 \\
    0  &\text{otherwise}\\
    \end{cases}
\]
for $i=1,\dots, n$.  In $\Lambda_p$, we use the sufficiently high precision 
of $10^5$ to impose the deterministic nature of the perturbation theory output.
In $\Lambda_\ell$, the multiplication by 16 accounts for the sample size of the
low resolution runs.
We then calculate a weighted average for each cosmology: 
$\bar y = \Lambda^{-1}(\Lambda_p y_p + \Lambda_{\ell} \bar{y}_\ell + \Lambda_h y_h)$, 
where $\Lambda = \Lambda_p + \Lambda_\ell + \Lambda_h$ and 
$\bar{y}_\ell = \frac{1}{16}\sum_{r=1}^{16} y_{\ell_r}$. In Figure \ref{fig:plot_data},
the weighted average is shown in dashed orange.  As an estimate of the true
underlying spectrum, the weighted average fluctuates too drastically.  
This is especially apparent after centering (right panel).
\textcolor{red}{(@Steve - how are we centering?)}
Although the weighted average incorporates all available observatons and 
expert knowledge regarding the precisions, it fails to account for the spatial 
dependence inherent in the smooth but stochastic spectra, which is pivotal to 
effectively inferring the true spectrum.

@@

\subsection{Model Specification}
\label{sec:mod_spec}

@@

For both $\Sigma_S$ and $\Sigma_W$, we use Mat\`ern kernels with unit scale and
unique lengthscales,
\[
\begin{array}{l}
\Sigma_S(W)^{i,j} = k\left(||w_i - w_j||^2, \theta_S\right) \\[7pt]
\Sigma_W(X)^{i,j} = k\left(||x_i - x_j||^2, \theta_W\right)
\end{array}
\quad\textrm{where}\quad
k(d, \theta) = \left( 1 + \frac{\sqrt{5}d}{\sqrt{\theta}} + 
  \frac{5d^2}{3\theta}\right) \exp\left(-\frac{\sqrt{5}d}{\sqrt{\theta}}\right).
\]
In our one-dimensional setting, we embrace unit scale on $S$ to preserve parsimony 
and identifiability with $\theta_S$ \citep{zhang2004inconsistent}.
Unit scale on latent $W$ was recommended by \citet{sauer2023active} for similar reasons.

@@

We compare DGP.FCO to competing models with a simulation study where the underlying 
true curve is known. Following \cite{moran2024dpc}, we consider two test functions 
defined as
\[
\begin{aligned}
  f_1(x) &= m_1 \exp\left(-\frac{u_1x}{2}\right) * 
  \cos\left(x\sqrt{25-\left(\frac{u_1}{2}\right)^2}\right) - \frac{m_1x}{5}\\
  f_2(x) &= \exp\left(-m_2(x-3)^2\right) + 
  \exp\left(-u_2(x-1)^2\right)-0.05\sin\left(8(x-1.9))\right.
\end{aligned}
\]
For additional variation, the values of $m_1, m_2, u_1,$ and $u_2$ are randomly selected from
$m_1 \sim \text{Uniform}(0.5,1.5)$, $u_1 \sim \text{Uniform}(1.5,2.5)$, and $m_2,u_2 
\sim \text{Uniform}(0.6,1.4)$. The outputs of $f_1$ and $f_2$ (conditional on $m_1,u_1$ and 
$m_2,u_2$), determine the true function values for each simulation.

For each of the two true functions, we consider two variance settings $A$ and $B$, where 
matrices $\Sigma_A$ and $\Sigma_B$ have a Mat\'ern covariance function with a nugget of 
$10^{-8}$ and smoothness of 2.5. We obtain function realizations at $x=\{0, 0.1, \dots, 
3.9, 4.0\}$, so that each function draw contains $n=41$ observations. We draw $r$-many 
realizations from a GP with some mean ($f_1$ or $f_2$) and some spatially varying covariance
($\Sigma_A$ or $\Sigma_B$), where:

\[
\begin{aligned}
\Sigma_A &= 0.0225 * k(||x_i - x_j||^2, 0.01), \\
\Sigma_B &= s^\top Ms \quad\textrm{where}\quad M = 0.1 * k(||x_i - x_j||^2, 0.05)
\quad\textrm{and}\quad s = 1.5^{-x/2},
\end{aligned}
\]

where $k(\cdot,\cdot)$ is defined in Section \ref{sec:mod_spec}.  Within $\Sigma_B$, $s$ introduces
nonstationarity into the function realizations, more accurately matching the behavior of the 
CAMB and Mira-Titan motivating datasets.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{run_sim_f1A_f2B.png}
    \caption{Illustration of simulation output, each with $r=5$ function realizations. The true function
             is shown in solid green, while the gray lines and points indicate the realizations. 
             Left panel: function $f_1$, variance setting $A$. 
             Right panel: function $f_2$, variance setting $B$.}   
    \label{fig:run_sim_f1A_f2B}
\end{figure}

For each simulated function and variance specification, we consider 20 Monte Carlo repetitions
with re-randomized $m_1, m_2, u_1, u_2$.  We consider $r = 5$ and $r = 15$. Examples of such
simulation output are shown in Figure \ref{fig:run_sim_f1A_f2B}.

\begin{figure}[t]
    \centering
    \includegraphics[width=6in]{sims_logS.png}
    \caption{Boxplot of log scores (20 repetitions, lower is better) for each 
             simulated scenario.  Each column represents a function/covariance 
             pair, and each row shows results for batch sizes of either 
             5 (top) or 15 (bottom) realizations. \textcolor{red}{(This figure needs udpating.)}}
    \label{fig:sims_logS}
\end{figure}

The competing methods we consider are an out-of-the-box DGP fit using the 
\texttt{deepgp} package \citep{sauer2023active}, a heteroskedastic GP fit using 
the \texttt{hetGP} package \citep{binois2018practical, binois2021hetgp}, as well 
as a deep process convolution (DPC) approach, which is utilized within Cosmic 
Emu \citep{moran2023mira}. These competing methods view the inputs as noisy observations
(i.e., the points in Figure \ref{fig:run_sim_f1A_f2B}) with no spatial dependence. In
contrast, our method uses the $r$ functional realizations to estimate parameters
within $\Sigma_\epsilon$ that account for the spatial dependence.

The metric we highlight to evaluate performance of each method is the
log score, a proper scoring rule which takes both prediction and intervals into 
consideration \citep{gneiting2007strictly}. A lower value indicates 
better performance. Log score are shown in Figure \ref{fig:sims_logS}; our DGP.FCO 
model performs favorably against each of these current benchmark methods by
accounting for spatial dependence within our model, resulting in more accurate UQ.
Mean squared error (MSE) results, which do not address UQ, were comparable across 
competing methods; these results can be found in Figure \ref{fig:sims_MSE}.

@@

We next investigate model fits to several cosmological 
datasets from CAMB \citep{lewis2011CAMB}. These datasets contain power spectra based
on six-dimensional cosmological parameter settings. Similar to the Mira-Titan suite, the
CAMB dataset contains data for sixty-four cosmologies, with each containing multiple 
(fifteen) low-resolution spectra, and one high-resolution spectrum. 
Unlike the Mira-Titan suite, this dataset additionally contains an infinite-resolution 
spectrum, which can be treated as the true spectrum for each cosmology,
allowing us to assess the accuracy of posterior mean estimates and effectiveness
of credible intervals. An illustration of the first cosmology from CAMB is shown
in Figure \ref{fig:fit_camb}, where the infinite-resolution spectrum is generally
much smoother than the low- and high-resolution counterparts.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{CAMB_fit_model1.png}
    \caption{Example of DGP.FCO model fit for the first batch of model runs from the CAMB data, 
             with a LOESS mean of the weighted average subtracted to emphasize details. We can 
             compare the orange lines (posterior mean and dotted 95\% credible interval) to the 
             light blue line, representing the infinite-resolution ``true" spectrum.}   
    \label{fig:fit_camb}
\end{figure}

Our goal here is to train the DGP.FCO model and accurately estimate the true spectrum for each
cosmology. To imitate the role of the perturbation theory output of Mira-Titan, we anchor 
estimates of the CAMB power spectrum at the infinite-resolution for $\log_{10}(k) < -1.7$, and 
then rely strictly on the low- and high-resolution runs for $k$ above this (note the transition
area in Figure \ref{fig:fit_camb} around the transformed $k$ value of 0.2). We first use a log-log 
regression model to obtain precision estimates $\Lambda_\ell$ and $\Lambda_h$
for the low- and high-resolution runs respectively, as outlined in Section \ref{sec:data}. 
Similarly, we set $\Lambda_c^{(ii)}=10^8$ when $\log_{10}(k_i) < -1.7$ ($0$ otherwise) for $i = 1,\dots,n$.
\textcolor{red}{(why switch from $10^5$ to $10^8$?)} 
to illustrate high confidence in the infinite-resolution run for low $k$ values.
We then take a weighted average of the CAMB runs in a similar fashion
to Mira-Titan data as described in Section \ref{sec:data}: $\bar y = \Lambda^{-1}(\Lambda_c y_c + 
\Lambda_{\ell} \bar{y}_\ell + \Lambda_h y_h)$, where $\Lambda = \Lambda_p + \Lambda_\ell + \Lambda_h$ 
and $\bar{y}_\ell = \frac{1}{15}\sum_{r=1}^{15} y_{\ell_r}$.

With weighted average and precision information, we considered a Mat\'ern kernel for 
$\Sigma_\varepsilon$. 
\textcolor{red}{(Yes, using maximum likelihood estimation with smoothness set to $5/2$, 
and we use $\tau^2$ and $\theta$ estimates here, in the sims, and for Mira-Titan; 
these estimates are coming out of the ``opt\_matern" function we created.)}
For the CAMB data, spatial correlation decays very quickly
($\theta\approx 0$ for CAMB, compare the smoothly varying low-resolution runs of 
Figure \ref{fig:fit_camb} with the jagged low-resolution CAMB runs in Figure \ref{fig:plot_data}). 
We therefore assume no spatial dependence for CAMB and specify $\Sigma_\varepsilon = 
(\Lambda_c+\Lambda_\ell+\Lambda_h)^{-1}$.

@@

\textcolor{red}{As of now, we are not comparing to DPC/hetGP/deepgp here, so no
MSE or log scores. We do have MSEs of CAMB predictions when training on these posterior means
vs training on the infinite-resolution runs; this comes up in Figures \ref{fig:pca_preds_v_camb} 
and \ref{fig:mse_camb} later.}

@@

From plots of the multiple low-resolution spectra (e.g., Figure \ref{fig:plot_data}), 
we find they vary smoothly about some mean $S$, suggesting that a dense covariance 
matrix $\Sigma_\varepsilon$ (accounting for domain knowledge and spatial dependence) 
may outperform a diagonal covariance $\Lambda_\ell^{-1}$ for $\bar Y$. From Section 
\ref{sec:data}, we can incorporate domain knowledge from $\Lambda_p, \Lambda_\ell,$ 
and $\Lambda_h$ within our model, and calculate the weighted average for each cosmology: 
$\bar y = \Lambda^{-1}(\Lambda_p y_p + \Lambda_{\ell} \bar{y}_\ell + \Lambda_h y_h)$, 
where $\Lambda = \Lambda_p + \Lambda_\ell + \Lambda_h$. 
In previous work, we have modeled multiple candidates for 
$\Sigma_\varepsilon$ \citep{walsh2023bayesian} and found that a Mat\'ern covariance 
$\Sigma_\ell$ trained on the low-resolution runs (pre-scaled by the precision 
values and subtracting a LOESS-smoothed average) performs the best. 
We specify this structure within $\Sigma_\varepsilon$ and refer readers 
to \cite{walsh2023bayesian} for a more detailed exposition. This yields 
$\Sigma_\varepsilon=\left(\Lambda_p^{-1} + \Sigma_\ell + \Lambda_h^{-1}\right)^{-1}$, 
where $\Lambda_p, \Sigma_\ell^{-1}, \text{ and } \Lambda_h$ are all $n\times n$ 
and are 0 wherever the corresponding data type is biased. From here, we estimate 
$\tau_\ell, \theta_\ell$ with maximum likelihood, and input these within 
$\Sigma_\varepsilon$, which we use as an input to our model.

@@

From these samples, we can estimate and quantify the uncertainty within each 
cosmology's average and latent layer $W$. Figure \ref{fig:plot_fit} shows an 
example of the uncertainty for our posterior mean for the first (of 111) training 
cosmologies; the posterior mean is subtracted in order to visualize this uncertainty. 
The UQ from the DGP.FCO model accounts for varying precisions across differing $k$ 
values, as well as the spatial correlation within the functional realizations.
Figure \ref{fig:plot_warp} provides elliptical slice samples of $W$ along with the 
average warping. From these samples, we see some departure from stationarity 
estimated in the higher $X$ (i.e., scaled $k$) values.

@@

\begin{figure}[ht]
   \centering
   \includegraphics[width=6in]{plot_warp_M001.png}
   \caption{Left: MCMC samples of $W$ for model M001 after burnin and thinning. 
            Right: Corresponding 95\% credible intervals for $W$, where departure 
            from the identity line represents nonstationary behavior.
            \textcolor{red}{(This plot needs to be made fresh (not using the package
             function.  Adjust y-axis.  We don't need the yellow/red coloring.)}}
   \label{fig:plot_warp}
\end{figure}
